---
title: "Maps Table"
author: "Gabriel de Freitas Pereira"
date: "01/07/2021"
output: html_document
---

<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(leaflet)
library(htmltools)
library(raster)
library(leaflegend)
library(leafletCN)
```

# Maps with geoglyphs and terra-preta

### Suitability Map - Geographical Filtering WorldClim 2.1 (CMIP6)

AUC = 0.87

```{r, warning=FALSE, echo=FALSE, message=FALSE, eval=TRUE}

#importing data from the geographical models using geoglyphs and tp_avg_aggr:
presence_2_5 <- raster("./vif_vars_geog/geog 2.5 tp_avg_aggr and geoglyphs vif/ensembles/presence/Bertholletia excelsa_present.tif")
presence_2_5[presence_2_5 == 0] <- NA

suitability_2_5 <- raster("./vif_vars_geog/geog 2.5 tp_avg_aggr and geoglyphs vif/ensembles/suitability/Bertholletia excelsa_present.tif")
suitability_2_5 <- mask(suitability_2_5, presence_2_5)

#building colors gradient:
fun <- colorRampPalette(c("#FF5948","#FEFC00", "#2C7202"))
#determining the values range according with the raster used:
cc <- fun(413)
#building palette to be used into leaflet():
pal <- colorNumeric(palette = cc,values(suitability_2_5), na.color = "transparent")
#building the map
A <- leaflet() %>%
  addProviderTiles(providers$OpenStreetMap) %>%
  setView(lng = -55.0, lat = -5, zoom = 4) %>%
  addRasterImage(suitability_2_5, opacity = 0.6, 
                 colors = pal) %>%  
  addLegend(position = "bottomright", pal = pal, values = values(suitability_2_5),
            opacity = 1, title = "Presence </br> suitability </br> (558 - 971)")
  

## Future Projections - SSP245
 
#CMIP6 data. 

ssp245_6mods_ <- raster("./futur3/combined_maps_g/Bertholletia excelsa_ssp245_2041_2060_change_6mods.tif")
pal <- colorFactor(palette = c("red","green","blue"), domain = values(ssp245_6mods_), na.color = "transparent")
labels <- c("Unsuitable","Remain suitable","Become suitable")

B <- leaflet() %>% 
  addProviderTiles(providers$OpenStreetMap) %>%
  setView(lng = -55.0, lat = -5, zoom = 4) %>%
  addRasterImage(ssp245_6mods_, opacity = 0.6, 
                 colors = pal, project = FALSE) %>% 
  addLegend(position = "bottomright", pal = pal, values = values(ssp245_6mods_), 
            opacity = 1, labFormat = function(type,cuts,p){paste0(labels)}, 
            title = "Presence suitability  <p> 6mods - ssp245")


## Future Projections - SSP585

#CMIP6 data. For more details click [here](https://bideco.shinyapps.io/futur3/).


ssp585_6mods_ <- raster("./futur3/combined_maps_g/Bertholletia excelsa_ssp585_2041_2060_change_6mods.tif") 
pal <- colorFactor(palette = c("red","green"), domain = values(ssp585_6mods_), na.color = "transparent")
labels <- c("Unsuitable","Remain suitable")

C <- leaflet() %>% 
  addProviderTiles(providers$OpenStreetMap) %>%
  setView(lng = -55.0, lat = -5, zoom = 4) %>%
  addRasterImage(ssp585_6mods_, opacity = 0.6, 
                 colors = pal, project = FALSE) %>% 
  addLegend(position = "bottomright", pal = pal, values = values(ssp585_6mods_), 
            opacity = 1, labFormat = function(type,cuts,p){paste0(labels)}, 
            title = "Presence suitability  <p> 6mods - ssp585")


leaflet_grid <-
  tagList(
  tags$table(width = "100%",
    tags$tr(
      tags$td(A),
      tags$td(B),
      tags$td(C)
    )
  )
)


leaflet_grid

```





### Suitability Map - Geographical Filtering WorldClim 1.4 LAM (CMIP5)

AUC = 0.88

```{r, warning=FALSE, echo=FALSE, message=FALSE, eval=TRUE}

#importing data from the geographical models using geoglyphs and tp_avg_aggr:
#presence points used for modelling / binary map 0 absence and 1 presence
presence_2_5 <- raster("./cmip5_prsent/geog 2.5 tp_avg_aggr and geoglyphs vif lam cmip5/ensembles/presence/Bertholletia excelsa_present.tif")
presence_2_5[presence_2_5 == 0] <- NA

#suitability map 0-1000:
suitability_2_5 <- raster("./cmip5_prsent/geog 2.5 tp_avg_aggr and geoglyphs vif lam cmip5/ensembles/suitability/Bertholletia excelsa_present.tif")
suitability_2_5 <- mask(suitability_2_5, presence_2_5)

fun <- colorRampPalette(c("#FF5948","#FEFC00", "#2C7202"))
#determining the values range according with the raster used:
cc <- fun(432)
#building palette to be used into leaflet():
pal <- colorNumeric(palette = cc,values(suitability_2_5), na.color = "transparent")
#building the map
A1 <- leaflet() %>%
  addProviderTiles(providers$OpenStreetMap) %>%
  setView(lng = -55.0, lat = -5, zoom = 4) %>%
  addRasterImage(suitability_2_5, opacity = 0.6, 
                 colors = pal) %>% 
  addLegend(position = "bottomright", pal = pal, values = values(suitability_2_5), 
            opacity = 1, title = "Presence </br> suitability </br> (539 - 971)")




## Future Projections - RCP45
 
#CMIP5 data. For more details click [here](https://bnutmodelling.shinyapps.io/future_cmip5/).

rcp45_3mods_ <- raster("./future_cmip5/combined_maps_g/Bertholletia excelsa_RCP45_2040_2069_change_3mods.tif")
pal <- colorFactor(palette = c("red","green","blue"), domain = values(rcp45_3mods_), na.color = "transparent")
labels <- c("Unsuitable","Remain suitable","Become suitable")

B1 <- leaflet() %>% 
  addProviderTiles(providers$OpenStreetMap) %>%
  setView(lng = -55.0, lat = -5, zoom = 4) %>%
  addRasterImage(rcp45_3mods_, opacity = 0.6, 
                 colors = pal, project = FALSE) %>% 
  addLegend(position = "bottomright", pal = pal, values = values(rcp45_3mods_), 
            opacity = 1, labFormat = function(type,cuts,p){paste0(labels)}, 
            title = "Presence suitability  <p> 3mods - rcp45")



## Future Projections - RCP85

#CMIP5 data. For more details click [here](https://bnutmodelling.shinyapps.io/future_cmip5/).

rcp85_3mods_ <- raster("./future_cmip5/combined_maps_g/Bertholletia excelsa_RCP85_2040_2069_change_3mods.tif")
pal <- colorFactor(palette = c("red","green","blue"), domain = values(rcp85_3mods_), na.color = "transparent")
labels <- c("Unsuitable","Remain suitable","Become suitable")

C1 <- leaflet() %>% 
  addProviderTiles(providers$OpenStreetMap) %>%
  setView(lng = -55.0, lat = -5, zoom = 4) %>%
  addRasterImage(rcp85_3mods_, opacity = 0.6, 
                 colors = pal, project = FALSE) %>% 
  addLegend(position = "bottomright", pal = pal, values = values(rcp85_3mods_), 
            opacity = 1, labFormat = function(type,cuts,p){paste0(labels)}, 
            title = "Presence suitability  <p> 3mods - rcp85")


leaflet_grid <-
  tagList(
  tags$table(width = "100%",
    tags$tr(
      tags$td(A1),
      tags$td(B1),
      tags$td(C1)
    )
  )
)


leaflet_grid


```


### Suitability Map - Geographical Filtering WorldClim 2.1 LAM (CMIP6) -

AUC = 0.88

```{r, warning=FALSE, echo=FALSE, message=FALSE, eval=TRUE}
presence_2_5 <- raster("./vif_vars_geog/geog 2.5 tp_avg_aggr and geoglyphs vif lam/ensembles/presence/Bertholletia excelsa_present.tif")
presence_2_5[presence_2_5 == 0] <- NA

#suitability map 0-1000:
suitability_2_5 <- raster("./vif_vars_geog/geog 2.5 tp_avg_aggr and geoglyphs vif lam/ensembles/suitability/Bertholletia excelsa_present.tif")
suitability_2_5 <- mask(suitability_2_5, presence_2_5)


fun <- colorRampPalette(c("#FF5948","#FEFC00", "#2C7202"))
#determining the values range according with the raster used:
cc <- fun(430)
#building palette to be used into leaflet():
pal <- colorNumeric(palette = cc,values(suitability_2_5), na.color = "transparent")
#building the map
A4 <- leaflet() %>%
  addProviderTiles(providers$OpenStreetMap) %>%
  setView(lng = -55.0, lat = -5, zoom = 4) %>%
  addRasterImage(suitability_2_5, opacity = 0.6, 
                 colors = pal) %>% 
  addLegend(position = "bottomright", pal = pal, values = values(suitability_2_5), 
            opacity = 1, title = "Presence </br> suitability </br> (539 - 969)")



## Future Projections - SSP245 LAM

#CMIP6 data. 

#geog 2.5 vif considering geoglyphs and tp:
ssp245_6mods_ <- raster("./vif_vars_geog/geog 2.5 tp_avg_aggr and geoglyphs vif lam/future projections/combined maps/Bertholletia excelsa_ssp245_2041_2060_change_6mods.tif")

#6 mods - 245
pal <- colorFactor(palette = c("red","green","blue"), domain = values(ssp245_6mods_), na.color = "transparent")
labels <- c("Unsuitable","Remain suitable","Become suitable")

B4 <- leaflet() %>% 
  addProviderTiles(providers$OpenStreetMap) %>%
  setView(lng = -55.0, lat = -5, zoom = 4) %>%
  addRasterImage(ssp245_6mods_, opacity = 0.6, 
                 colors = pal, project = FALSE) %>% 
  addLegend(position = "bottomright", pal = pal, values = values(ssp245_6mods_), 
            opacity = 1, labFormat = function(type,cuts,p){paste0(labels)}, 
            title = "Presence suitability  <p> 6mods - ssp245")




## Future Projections - SSP585 LAM

#CMIP6 data. For more details click [here](https://bnutmodelling.shinyapps.io/future_env/).

ssp585_6mods_ <- raster("./vif_vars_geog/geog 2.5 tp_avg_aggr and geoglyphs vif lam/future projections/combined maps/Bertholletia excelsa_ssp585_2041_2060_change_6mods.tif")

#6 mods - 585
pal <- colorFactor(palette = c("red","green"), domain = values(ssp585_6mods_), na.color = "transparent")
labels <- c("Unsuitable","Remain suitable")

C4 <- leaflet() %>% 
  addProviderTiles(providers$OpenStreetMap) %>%
  setView(lng = -55.0, lat = -5, zoom = 4) %>%
  addRasterImage(ssp585_6mods_, opacity = 0.6, 
                 colors = pal, project = FALSE) %>% 
  addLegend(position = "bottomright", pal = pal, values = values(ssp585_6mods_), 
            opacity = 1, labFormat = function(type,cuts,p){paste0(labels)}, 
            title = "Presence suitability  <p> 6mods - ssp585")



leaflet_grid <-
  tagList(
  tags$table(width = "100%",
    tags$tr(
      tags$td(A4),
      tags$td(B4),
      tags$td(C4)
    )
  )
)


leaflet_grid


```





### Suitability Map - Environmental Filtering Worldclim 2.1 (CMIP6)

AUC = 0.94

```{r, warning=FALSE, echo=FALSE, message=FALSE, eval=TRUE}
presence_2_5_ <- raster("./vif_vars_env/env 2.5 tp_avg_aggr and geoglyphs vif/ensembles/presence/Bertholletia excelsa_present.tif")
presence_2_5_[presence_2_5_ == 0] <- NA

#suitability map 0-1000:
suitability_2_5_ <- raster("./vif_vars_env/env 2.5 tp_avg_aggr and geoglyphs vif/ensembles/suitability/Bertholletia excelsa_present.tif")
suitability_2_5_ <- mask(suitability_2_5_, presence_2_5_)

fun <- colorRampPalette(c("#FF5948","#FEFC00", "#2C7202"))
#determining the values range according with the raster used:
cc <- fun(484)
#building palette to be used into leaflet():
pal <- colorNumeric(palette = cc,values(suitability_2_5_), na.color = "transparent")
#building the map
A2 <- leaflet() %>%
  addProviderTiles(providers$OpenStreetMap) %>%
  setView(lng = -55.0, lat = -5, zoom = 4) %>%
  addRasterImage(suitability_2_5_, opacity = 0.6, 
                 colors = pal) %>% 
  addLegend(position = "bottomright", pal = pal, values = values(suitability_2_5_), 
            opacity = 1, title = "Presence </br> suitability </br> (503 - 987)")



## Future Projections - SSP245

#CMIP6 data. For more details click [here](https://bnutmodelling.shinyapps.io/future_env/).

ssp245_6mods <- raster("./future_env/combined_maps_g_without_lam/Bertholletia excelsa_ssp245_2041_2060_change_6mods.tif")

pal <- colorFactor(palette = c("red","green","blue"), domain = values(ssp245_6mods), na.color = "transparent")
labels <- c("Unsuitable","Remain suitable","Become suitable")

B2 <- leaflet() %>% 
  addProviderTiles(providers$OpenStreetMap) %>%
  setView(lng = -55.0, lat = -5, zoom = 4) %>%
  addRasterImage(ssp245_6mods, opacity = 0.6, 
                 colors = pal, project = FALSE) %>% 
  addLegend(position = "bottomright", pal = pal, values = values(ssp245_6mods), 
            opacity = 1, labFormat = function(type,cuts,p){paste0(labels)}, 
            title = "Presence suitability  <p> 6mods - ssp245")



## Future Projections - SSP585

#CMIP6 data. For more details click [here](https://bnutmodelling.shinyapps.io/future_env/).

ssp585_6mods <- raster("./future_env/combined_maps_g_without_lam/Bertholletia excelsa_ssp585_2041_2060_change_6mods.tif")

#6 mods - 585
pal <- colorFactor(palette = c("red","green","blue"), domain = values(ssp585_6mods), na.color = "transparent")
labels <- c("Unsuitable","Remain suitable","Become suitable")

C2 <- leaflet() %>% 
  addProviderTiles(providers$OpenStreetMap) %>%
  setView(lng = -55.0, lat = -5, zoom = 4) %>%
  addRasterImage(ssp585_6mods, opacity = 0.6, 
                 colors = pal, project = FALSE) %>% 
  addLegend(position = "bottomright", pal = pal, values = values(ssp585_6mods), 
            opacity = 1, labFormat = function(type,cuts,p){paste0(labels)}, 
            title = "Presence suitability  <p> 6mods - ssp585")

leaflet_grid <-
  tagList(
  tags$table(width = "100%",
    tags$tr(
      tags$td(A2),
      tags$td(B2),
      tags$td(C2)
    )
  )
)


leaflet_grid


```



### Suitability Map - Environmental Filtering WorldClim 1.4 LAM (CMIP5) -

AUC = 0.90

```{r, warning=FALSE, echo=FALSE, message=FALSE, eval=TRUE}
presence_2_5 <- raster("./vif_vars_env/env 2.5 tp_avg_aggr and geoglyphs vif lam cmip5/ensembles/presence/Bertholletia excelsa_present.tif")
presence_2_5[presence_2_5 == 0] <- NA

#suitability map 0-1000:
suitability_2_5 <- raster("./vif_vars_env/env 2.5 tp_avg_aggr and geoglyphs vif lam cmip5/ensembles/suitability/Bertholletia excelsa_present.tif")
suitability_2_5 <- mask(suitability_2_5, presence_2_5)


fun <- colorRampPalette(c("#FF5948","#FEFC00", "#2C7202"))
#determining the values range according with the raster used:
cc <- fun(387)
#building palette to be used into leaflet():
pal <- colorNumeric(palette = cc,values(suitability_2_5), na.color = "transparent")
#building the map
A3 <- leaflet() %>%
  addProviderTiles(providers$OpenStreetMap) %>%
  setView(lng = -55.0, lat = -5, zoom = 4) %>%
  addRasterImage(suitability_2_5, opacity = 0.6, 
                 colors = pal) %>% 
  addLegend(position = "bottomright", pal = pal, values = values(suitability_2_5), 
            opacity = 1, title = "Presence </br> suitability </br> (587 - 974)")



## Future Projections - RCP45 LAM

#CMIP5 data. 

#env 2.5 vif considering geoglyphs and tp:
rcp45_4mods_ <- raster("./vif_vars_env/env 2.5 tp_avg_aggr and geoglyphs vif lam cmip5/future projections/combined maps/Bertholletia excelsa_RCP45_2040_2069_change_4mods.tif")

#4 mods - 45
pal <- colorFactor(palette = c("red","green"), domain = values(rcp45_4mods_), na.color = "transparent")
labels <- c("Unsuitable","Remain suitable")

B3 <- leaflet() %>% 
  addProviderTiles(providers$OpenStreetMap) %>% 
  setView(lng = -55.0, lat = -5, zoom = 4) %>%
  addRasterImage(rcp45_4mods_, opacity = 0.6, 
                 colors = pal, project = FALSE) %>% 
  addLegend(position = "bottomright", pal = pal, values = values(rcp45_4mods_), 
            opacity = 1, labFormat = function(type,cuts,p){paste0(labels)}, 
            title = "Presence suitability  <p> 4mods - rcp45")




## Future Projections - RCP85 LAM

#CMIP5 data. 

rcp85_4mods_ <- raster("./vif_vars_env/env 2.5 tp_avg_aggr and geoglyphs vif lam cmip5/future projections/combined maps/Bertholletia excelsa_RCP85_2040_2069_change_4mods.tif")

#4 mods - 85
pal <- colorFactor(palette = c("red","green","blue"), domain = values(rcp85_4mods_), na.color = "transparent")
labels <- c("Unsuitable","Remain suitable","Become suitable")

C3 <- leaflet() %>% 
  addProviderTiles(providers$OpenStreetMap) %>%
  setView(lng = -55.0, lat = -5, zoom = 4) %>%
  addRasterImage(rcp85_4mods_, opacity = 0.6, 
                 colors = pal, project = FALSE) %>% 
  addLegend(position = "bottomright", pal = pal, values = values(rcp85_4mods_), 
            opacity = 1, labFormat = function(type,cuts,p){paste0(labels)}, 
            title = "Presence suitability  <p> 4mods - rcp85")



leaflet_grid <-
  tagList(
  tags$table(width = "100%",
    tags$tr(
      tags$td(A3),
      tags$td(B3),
      tags$td(C3)
    )
  )
)


leaflet_grid


```


### Suitability Map - Environmental Filtering WorldClim 2.1 LAM (CMIP6)

AUC = 0.93

```{r, warning=FALSE, echo=FALSE, message=FALSE, eval=TRUE}

presence_2_5 <- raster("./vif_vars_env/env 2.5 tp_avg_aggr and geoglyphs vif lam/ensembles/presence/Bertholletia excelsa_present.tif")
presence_2_5[presence_2_5 == 0] <- NA

#suitability map 0-1000:
suitability_2_5 <- raster("./vif_vars_env/env 2.5 tp_avg_aggr and geoglyphs vif lam/ensembles/suitability/Bertholletia excelsa_present.tif")
suitability_2_5 <- mask(suitability_2_5, presence_2_5)


fun <- colorRampPalette(c("#FF5948","#FEFC00", "#2C7202"))
#determining the values range according with the raster used:
cc <- fun(392)
#building palette to be used into leaflet():
pal <- colorNumeric(palette = cc,values(suitability_2_5), na.color = "transparent")
#building the map
A4 <- leaflet() %>%
  addProviderTiles(providers$OpenStreetMap) %>%
  setView(lng = -55.0, lat = -5, zoom = 4) %>%
  addRasterImage(suitability_2_5, opacity = 0.6, 
                 colors = pal) %>% 
  addLegend(position = "bottomright", pal = pal, values = values(suitability_2_5), 
            opacity = 1, title = "Presence </br> suitability </br> (588 - 980)")



## Future Projections - SSP245 LAM

#CMIP6 data.

#env 2.5 vif considering geoglyphs and tp:
ssp245_6mods_ <- raster("./vif_vars_env/env 2.5 tp_avg_aggr and geoglyphs vif lam/future projections/combined maps/Bertholletia excelsa_ssp245_2041_2060_change_6mods.tif")

#6 mods - 245
pal <- colorFactor(palette = c("red","green","blue"), domain = values(ssp245_6mods_), na.color = "transparent")
labels <- c("Unsuitable","Remain suitable","Become suitable")

B4 <- leaflet() %>% 
  addProviderTiles(providers$OpenStreetMap) %>%
  setView(lng = -55.0, lat = -5, zoom = 4) %>%
  addRasterImage(ssp245_6mods_, opacity = 0.6, 
                 colors = pal, project = FALSE) %>% 
  addLegend(position = "bottomright", pal = pal, values = values(ssp245_6mods_), 
            opacity = 1, labFormat = function(type,cuts,p){paste0(labels)}, 
            title = "Presence suitability  <p> 6mods - ssp245")




## Future Projections - SSP585 LAM

#CMIP6 data. 

ssp585_6mods_ <- raster("./vif_vars_env/env 2.5 tp_avg_aggr and geoglyphs vif lam/future projections/combined maps/Bertholletia excelsa_ssp585_2041_2060_change_6mods.tif")

#6 mods - 585
pal <- colorFactor(palette = c("red","green","blue"), domain = values(ssp585_6mods_), na.color = "transparent")
labels <- c("Unsuitable","Remain suitable","Become suitable")

C4 <- leaflet() %>% 
  addProviderTiles(providers$OpenStreetMap) %>%
  setView(lng = -55.0, lat = -5, zoom = 4) %>%
  addRasterImage(ssp585_6mods_, opacity = 0.6, 
                 colors = pal, project = FALSE) %>% 
  addLegend(position = "bottomright", pal = pal, values = values(ssp585_6mods_), 
            opacity = 1, labFormat = function(type,cuts,p){paste0(labels)}, 
            title = "Presence suitability  <p> 6mods - ssp585")



leaflet_grid <-
  tagList(
  tags$table(width = "100%",
    tags$tr(
      tags$td(A4),
      tags$td(B4),
      tags$td(C4)
    )
  )
)


leaflet_grid


```



# Maps without geoglyphs and terra-preta:

### Suitability Map - Geographical Filtering WorldClim 2.1 LAM (CMIP6)

```{r, warning=FALSE, echo=FALSE, message=FALSE, eval=TRUE}
presence_2_5 <- raster("./vif_vars_geog/geog 2.5 vif no terrapreta lam/ensembles/presence/Bertholletia excelsa_present.tif")
presence_2_5[presence_2_5 == 0] <- NA

#suitability map 0-1000:
suitability_2_5 <- raster("./vif_vars_geog/geog 2.5 vif no terrapreta lam/ensembles/suitability/Bertholletia excelsa_present.tif")
suitability_2_5 <- mask(suitability_2_5, presence_2_5)


fun <- colorRampPalette(c("#FF5948","#FEFC00", "#2C7202"))
#determining the values range according with the raster used:
cc <- fun(431)
#building palette to be used into leaflet():
pal <- colorNumeric(palette = cc,values(suitability_2_5), na.color = "transparent")
#building the map
A4 <- leaflet() %>%
  addProviderTiles(providers$OpenStreetMap) %>%
  setView(lng = -55.0, lat = -5, zoom = 4) %>%
  addRasterImage(suitability_2_5, opacity = 0.6, 
                 colors = pal) %>% 
  addLegend(position = "bottomright", pal = pal, values = values(suitability_2_5), 
            opacity = 1, title = "Presence </br> suitability </br> (537 - 968)")



## Future Projections - SSP245 LAM

#CMIP6 data. 

#env 2.5 vif considering geoglyphs and tp:
ssp245_6mods_ <- raster("./vif_vars_geog/geog 2.5 vif no terrapreta lam/future projections/combined maps/Bertholletia excelsa_ssp245_2041_2060_change_6mods.tif")

#6 mods - 245
pal <- colorFactor(palette = c("red","green","blue"), domain = values(ssp245_6mods_), na.color = "transparent")
labels <- c("Unsuitable","Remain suitable","Become suitable")

B4 <- leaflet() %>% 
  addProviderTiles(providers$OpenStreetMap) %>%
  setView(lng = -55.0, lat = -5, zoom = 4) %>%
  addRasterImage(ssp245_6mods_, opacity = 0.6, 
                 colors = pal, project = FALSE) %>% 
  addLegend(position = "bottomright", pal = pal, values = values(ssp245_6mods_), 
            opacity = 1, labFormat = function(type,cuts,p){paste0(labels)}, 
            title = "Presence suitability  <p> 6mods - ssp245")




## Future Projections - SSP585 LAM

#CMIP6 data. 

ssp585_6mods_ <- raster("./vif_vars_geog/geog 2.5 vif no terrapreta lam/future projections/combined maps/Bertholletia excelsa_ssp585_2041_2060_change_6mods.tif")

#6 mods - 585
pal <- colorFactor(palette = c("red","green","blue"), domain = values(ssp585_6mods_), na.color = "transparent")
labels <- c("Unsuitable","Remain suitable","Become suitable")

C4 <- leaflet() %>% 
  addProviderTiles(providers$OpenStreetMap) %>%
  setView(lng = -55.0, lat = -5, zoom = 4) %>%
  addRasterImage(ssp585_6mods_, opacity = 0.6, 
                 colors = pal, project = FALSE) %>% 
  addLegend(position = "bottomright", pal = pal, values = values(ssp585_6mods_), 
            opacity = 1, labFormat = function(type,cuts,p){paste0(labels)}, 
            title = "Presence suitability  <p> 6mods - ssp585")



leaflet_grid <-
  tagList(
  tags$table(width = "100%",
    tags$tr(
      tags$td(A4),
      tags$td(B4),
      tags$td(C4)
    )
  )
)


leaflet_grid


```


### Suitability Map - Geographical Filtering WorldClim 1.4 LAM (CMIP5)

```{r, warning=FALSE, echo=FALSE, message=FALSE, eval=TRUE}


presence_2_5 <- raster("./vif_vars_geog/geog 2.5 vif no terrapreta lam cmip5/ensembles/presence/Bertholletia excelsa_present.tif")
presence_2_5[presence_2_5 == 0] <- NA

#suitability map 0-1000:
suitability_2_5 <- raster("./vif_vars_geog/geog 2.5 vif no terrapreta lam cmip5/ensembles/suitability/Bertholletia excelsa_present.tif")
suitability_2_5 <- mask(suitability_2_5, presence_2_5)


fun <- colorRampPalette(c("#FF5948","#FEFC00", "#2C7202"))
#determining the values range according with the raster used:
cc <- fun(397)
#building palette to be used into leaflet():
pal <- colorNumeric(palette = cc,values(suitability_2_5), na.color = "transparent")
#building the map
A4 <- leaflet() %>%
  addProviderTiles(providers$OpenStreetMap) %>%
  setView(lng = -55.0, lat = -5, zoom = 4) %>%
  addRasterImage(suitability_2_5, opacity = 0.6, 
                 colors = pal) %>% 
  addLegend(position = "bottomright", pal = pal, values = values(suitability_2_5), 
            opacity = 1, title = "Presence </br> suitability </br> (568 - 965)")



## Future Projections - SSP245 LAM

#CMIP5 data. 

#geog 2.5 vif
rcp45_4mods_ <- raster("./vif_vars_geog/geog 2.5 vif no terrapreta lam cmip5/future projections/combined maps/Bertholletia excelsa_RCP45_2040_2069_change_4mods.tif")

#4 mods - 45
pal <- colorFactor(palette = c("red","green","blue"), domain = values(rcp45_4mods_), na.color = "transparent")
labels <- c("Unsuitable","Remain suitable","Become suitable")

B4 <- leaflet() %>% 
  addProviderTiles(providers$OpenStreetMap) %>%
  setView(lng = -55.0, lat = -5, zoom = 4) %>%
  addRasterImage(rcp45_4mods_, opacity = 0.6, 
                 colors = pal, project = FALSE) %>% 
  addLegend(position = "bottomright", pal = pal, values = values(rcp45_4mods_), 
            opacity = 1, labFormat = function(type,cuts,p){paste0(labels)}, 
            title = "Presence suitability  <p> 4mods - rcp45")




## Future Projections - RCP85 LAM

#CMIP5 data. 

rcp85_4mods_ <- raster("./vif_vars_geog/geog 2.5 vif no terrapreta lam cmip5/future projections/combined maps/Bertholletia excelsa_RCP85_2040_2069_change_4mods.tif")

#4 mods - 85
pal <- colorFactor(palette = c("red","green","blue"), domain = values(rcp85_4mods_), na.color = "transparent")
labels <- c("Unsuitable","Remain suitable","Become suitable")

C4 <- leaflet() %>% 
  addProviderTiles(providers$OpenStreetMap) %>%
  setView(lng = -55.0, lat = -5, zoom = 4) %>%
  addRasterImage(rcp85_4mods_, opacity = 0.6, 
                 colors = pal, project = FALSE) %>% 
  addLegend(position = "bottomright", pal = pal, values = values(rcp85_4mods_), 
            opacity = 1, labFormat = function(type,cuts,p){paste0(labels)}, 
            title = "Presence suitability  <p> 4mods - rcp85")



leaflet_grid <-
  tagList(
  tags$table(width = "100%",
    tags$tr(
      tags$td(A4),
      tags$td(B4),
      tags$td(C4)
    )
  )
)


leaflet_grid


```



### Suitability Map - Environmental Filtering WorldClim 2.1 LAM (CMIP6)



```{r, warning=FALSE, echo=FALSE, message=FALSE, eval=TRUE}
presence_2_5_ <- raster("./vif_vars_env/env 2.5 vif no terrapreta lam/ensembles/presence/Bertholletia excelsa_present.tif")
presence_2_5_[presence_2_5_ == 0] <- NA

#suitability map 0-1000:
suitability_2_5_ <- raster("./vif_vars_env/env 2.5 vif no terrapreta lam/ensembles/suitability/Bertholletia excelsa_present.tif")
suitability_2_5_ <- mask(suitability_2_5_, presence_2_5_)

fun <- colorRampPalette(c("#FF5948","#FEFC00", "#2C7202"))
#determining the values range according with the raster used:
cc <- fun(427)
#building palette to be used into leaflet():
pal <- colorNumeric(palette = cc,values(suitability_2_5_), na.color = "transparent")
#building the map
A2 <- leaflet() %>%
  addProviderTiles(providers$OpenStreetMap) %>%
  setView(lng = -55.0, lat = -5, zoom = 4) %>%
  addRasterImage(suitability_2_5_, opacity = 0.6, 
                 colors = pal) %>% 
  addLegend(position = "bottomright", pal = pal, values = values(suitability_2_5_), 
            opacity = 1, title = "Presence </br> suitability </br> (550 - 977)")



## Future Projections - SSP245

#CMIP6 data. 

ssp245_6mods <- raster("./vif_vars_env/env 2.5 vif no terrapreta lam/future projections/combined maps/Bertholletia excelsa_ssp245_2041_2060_change_6mods.tif")

pal <- colorFactor(palette = c("red","green","blue"), domain = values(ssp245_6mods), na.color = "transparent")
labels <- c("Unsuitable","Remain suitable","Become suitable")

B2 <- leaflet() %>% 
  addProviderTiles(providers$OpenStreetMap) %>%
  setView(lng = -55.0, lat = -5, zoom = 4) %>%
  addRasterImage(ssp245_6mods, opacity = 0.6, 
                 colors = pal, project = FALSE) %>% 
  addLegend(position = "bottomright", pal = pal, values = values(ssp245_6mods), 
            opacity = 1, labFormat = function(type,cuts,p){paste0(labels)}, 
            title = "Presence suitability  <p> 6mods - ssp245")



## Future Projections - SSP585

#CMIP6 data. 

ssp585_6mods <- raster("./vif_vars_env/env 2.5 vif no terrapreta lam/future projections/combined maps/Bertholletia excelsa_ssp585_2041_2060_change_6mods.tif")

#6 mods - 585
pal <- colorFactor(palette = c("red","green","blue"), domain = values(ssp585_6mods), na.color = "transparent")
labels <- c("Unsuitable","Remain suitable","Become suitable")

C2 <- leaflet() %>% 
  addProviderTiles(providers$OpenStreetMap) %>%
  setView(lng = -55.0, lat = -5, zoom = 4) %>%
  addRasterImage(ssp585_6mods, opacity = 0.6, 
                 colors = pal, project = FALSE) %>% 
  addLegend(position = "bottomright", pal = pal, values = values(ssp585_6mods), 
            opacity = 1, labFormat = function(type,cuts,p){paste0(labels)}, 
            title = "Presence suitability  <p> 6mods - ssp585")

leaflet_grid <-
  tagList(
  tags$table(width = "100%",
    tags$tr(
      tags$td(A2),
      tags$td(B2),
      tags$td(C2)
    )
  )
)


leaflet_grid


```


### Suitability Map - Environmental Filtering WorldClim 1.4 LAM (CMIP5)

```{r, warning=FALSE, echo=FALSE, message=FALSE, eval=TRUE}
presence_2_5 <- raster("./vif_vars_env/env 2.5 vif no terrapreta LAM cmip5/ensembles/presence/Bertholletia excelsa_present.tif")
presence_2_5[presence_2_5 == 0] <- NA

#suitability map 0-1000:
suitability_2_5 <- raster("./vif_vars_env/env 2.5 vif no terrapreta LAM cmip5/ensembles/suitability/Bertholletia excelsa_present.tif")
suitability_2_5 <- mask(suitability_2_5, presence_2_5)


fun <- colorRampPalette(c("#FF5948","#FEFC00", "#2C7202"))
#determining the values range according with the raster used:
cc <- fun(400)
#building palette to be used into leaflet():
pal <- colorNumeric(palette = cc,values(suitability_2_5), na.color = "transparent")
#building the map
A3 <- leaflet() %>%
  addProviderTiles(providers$OpenStreetMap) %>%
  setView(lng = -55.0, lat = -5, zoom = 4) %>%
  addRasterImage(suitability_2_5, opacity = 0.6, 
                 colors = pal) %>% 
  addLegend(position = "bottomright", pal = pal, values = values(suitability_2_5), 
            opacity = 1, title = "Presence </br> suitability </br> (574 - 974)")



## Future Projections - RCP45 LAM

#CMIP5 data. 

#env 2.5 vif considering geoglyphs and tp:
rcp45_4mods_ <- raster("./vif_vars_env/env 2.5 vif no terrapreta LAM cmip5/future projections/combined maps/Bertholletia excelsa_RCP45_2040_2069_change_4mods.tif")

#4 mods - 45
pal <- colorFactor(palette = c("red","green","blue"), domain = values(rcp45_4mods_), na.color = "transparent")
labels <- c("Unsuitable","Remain suitable","Become suitable")

B3 <- leaflet() %>% 
  addProviderTiles(providers$OpenStreetMap) %>%
  setView(lng = -55.0, lat = -5, zoom = 4) %>%
  addRasterImage(rcp45_4mods_, opacity = 0.6, 
                 colors = pal, project = FALSE) %>% 
  addLegend(position = "bottomright", pal = pal, values = values(rcp45_4mods_), 
            opacity = 1, labFormat = function(type,cuts,p){paste0(labels)}, 
            title = "Presence suitability  <p> 4mods - rcp45")




## Future Projections - RCP85 LAM

#CMIP5 data. 

rcp85_4mods_ <- raster("./vif_vars_env/env 2.5 tp_avg_aggr and geoglyphs vif lam cmip5/future projections/combined maps/Bertholletia excelsa_RCP85_2040_2069_change_4mods.tif")

#4 mods - 85
pal <- colorFactor(palette = c("red","green","blue"), domain = values(rcp85_4mods_), na.color = "transparent")
labels <- c("Unsuitable","Remain suitable","Become suitable")

C3 <- leaflet() %>% 
  addProviderTiles(providers$OpenStreetMap) %>%
  setView(lng = -55.0, lat = -5, zoom = 4) %>%
  addRasterImage(rcp85_4mods_, opacity = 0.6, 
                 colors = pal, project = FALSE) %>% 
  addLegend(position = "bottomright", pal = pal, values = values(rcp85_4mods_), 
            opacity = 1, labFormat = function(type,cuts,p){paste0(labels)}, 
            title = "Presence suitability  <p> 4mods - rcp85")



leaflet_grid <-
  tagList(
  tags$table(width = "100%",
    tags$tr(
      tags$td(A3),
      tags$td(B3),
      tags$td(C3)
    )
  )
)


leaflet_grid


```

